---
title: "Importing/Exporting of Data"
author: "Joyce F. Jamile"
subtitle: Use of MySQL
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Creating connections

+ You must have a database first before connecting the RStudio into a database. Depending on the database, a package should be installed like **RMySQL**, **RPostGre**, **MariaDB** to name a few.

> `dbConnect()` is being used to connect the R into MySQL

```{r library}
library(dplyr,dbplyr)
library(RMySQL)
library(RMariaDB)
library(tidyverse)
```

```{r creating connections}

#creating connections
connection <- dbConnect(RMariaDB::MariaDB(), 
                        dsn="MySQL-connection",
                        Server = "localhost",
                        dbname = "arxivdb", 
                        user = "root", 
                        password = "") #PWD is the password of your MySQL
```

```{r import table}
# Importing data from CSV into arxivPapers
arxivPapers <- as_tibble(read.csv("ArxivPapersOnTextMIning.csv"))

dbWriteTable(connection, "new_arxivdata_table", arxivPapers, overwrite = TRUE)

```


### Listing the tables

+ Once connected, `dbListTables` to show or list the tables.



```{r}
#listing the tables of the sample_db 
dbListTables(connection)
```


```{r}
#listing the fields of the authors in the table sample_db
dbListFields(connection,"arxivdata")
```


```{r}
dbListFields(connection,"arxivdata")
```


### Getting data from MySQL

+ using the *`dbGetQuery`* is beinng used to get the data

+ SQL commands were `SELECT` and `FROM`


```{r}
posts_dta <- dbGetQuery(connection, "SELECT * FROM arxivdb.arxivdata")
# checking for the columns and its content
glimpse(posts_dta)
```

```{r}
#getting all data using SELECT * FROM arxivdb
glimpse(empi_data)
```


```{r}
#getting all data using SELECT * FROM dbaseName
empi_data[c(1:10),]
```

```{r}
empi_data <- dbGetQuery(connection, "SELECT * FROM arxivdb.authors")
tail(empi_data)
```

```{r}
#alternative way to display selected fields
#displays the selected fields of the table
posts_data <- dbGetQuery(connection, "SELECT title,abstract FROM arxivdb.arxivdata")
posts_data[c(1:2),]
```

```{r}
#getting all data using SELECT * FROM dbaseName
SqlQuery <- "
  SELECT title,abstract
  FROM arxivdata
  "

as_tibble(dbGetQuery(connection,SqlQuery))
```

### Inserting values into a Table

```{r}
for (i in 1:150) {
  current_row <- arxivPapers[i, ]

  # Quote and escape string values using dbQuoteString
  title <- dbQuoteString(connection, current_row$title)
  author <- dbQuoteString(connection, current_row$author)
  subject <- dbQuoteString(connection, current_row$subject)
  abstract <- dbQuoteString(connection, current_row$abstract)
  meta <- dbQuoteString(connection, current_row$meta)

  # Create an INSERT INTO query
  query <- ("INSERT INTO arxivdata (title, author, subject, abstract, meta) VALUES ({title}, {author}, {subject}, {abstract}, {meta})")


  query_result <- dbSendQuery(connection, query)
  dbClearResult(query_result)
}

```


```{r}
#checking if the value was inserted into a table
tail(empi_data)
```
```{r}
#disconnect from dbase
dbDisconnect(connection)
```